### 2017-10-31 monograph/thesis/chapters/introduction.tex
Created the reference for Purposes, Concepts, Misfits, and a
Redesign of Git.
Created the references Code Scanning Patterns in Program
Comprehension and Code Classification as a Learning and Assessment
Exercise for Novice Programmers.
Created the reference Debugging into Examples debuggingIntoExamples
Created the reference to The Use of Reading Technique and
Visualization for Program Understanding, programUnderstanding.
Created the reference Documenting and sharing knowledge about code,
documentingAndSharingKnowledge.
Created the reference to Analysis of code reading to gain more
insight in pr

    Application fields for code beautifiers:
    \cite{annotationAssistant}
    \cite{codePlagiarismDetection}
    \cite{softwarePortfolio}
    \cite{legacyAssets}
    \cite{massMaintenance}
    \cite{prettyPrinting}
    \cite{architectureFormatting}
    \cite{independentFramework}
    \cite{programIndentation}
    \cite{industrialApplication}
    \cite{toolsForProjectManagement}

@@

@@

    Variables naming are extremely important. That is it, a dot.

>>>>

    Application fields for code beautifiers:
    \citeonline{annotationAssistant},
    \citeonline{codePlagiarismDetection},
    \citeonline{softwarePortfolio},
    \citeonline{legacyAssets},
    \citeonline{massMaintenance},
    \citeonline{prettyPrinting},
    \citeonline{architectureFormatting},
    \citeonline{independentFramework},
    \citeonline{programIndentation},
    \citeonline{industrialApplication},
    \citeonline{toolsForProjectManagement},
    \citeonline{codeClassification},
    \citeonline{codeScanningPatterns},
    \citeonline{debuggingIntoExamples},
    \citeonline{programUnderstanding},
    \citeonline{documentingAndSharingKnowledge},

@@

    Do related and small commits, i.e., one change per commit.

    What is upstream?

    \url{https://help.github.com/articles/configuring-a-remote-for-a-fork/}

    \url{https://stackoverflow.com/questions/2739376/definition-of-downstream-and-upstream}

    What is origin?

    Is there a downstream?

    \citeonline{redesignOfGit}

@@

    Variables naming are extremely important. That is it, a dot. By the article
    \citeonline{analysisOfCodeReading} there is the understanding about tracking
    techniques to improve code comprehension by closing the program code with
    natural language, i.e., as long as your code looks like natural language
    text, better would be your understanding of the code.
